---
title: "Hedonic Home Price Prediction"
author: "Jonathon Sun, Johnathan Clementi"
date: "9/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = TRUE)
pacman::p_load(tidyverse, tidycensus, sf, kableExtra, tmap, viridis, gridExtra, spdep, caret, ckanr, FNN, grid, gridExtra, ggcorplot, httr, sf)

options(scipen = 999)
options(scipen =  "sf")


source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

palette5 <- c("#25CB10", "#5AB60C", "#8FA108",   "#C48C04", "#FA7800")
```

## Pulling Data

```{r message=FALSE, warning=FALSE}
studentData.training <- st_read("studentData.geojson", crs = 'ESRI:102254') %>%
  filter(toPredict == 0) %>% 
  st_transform('ESRI:102653')

```


### Census 2019

Look for zip codes not census tracts, because who purchases by census tracts?


```{r tidycensus_2019, echo=FALSE}

#variables on frequency of Race
Variables <- load_variables(2019,
                            "acs5",
                            cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("RACE", concept)) %>%
  filter(!grepl("AGE", concept)) %>%
  slice(1:10)

#variable median age, men and women not by race
A <- load_variables(2019,
                    "acs5",
                    cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("MEDIAN", concept)) %>%
  slice(1:3)

#Median Household Income
B <- load_variables(2019,
                    "acs5",
                    cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("MEDIAN INCOME", concept)) %>%
  slice(1)

# Cost of living
C <- load_variables(2019,
                    "acs5",
                    cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("COST", concept)) %>%
  slice(1:19)

Variables <- bind_rows(Variables, A, B, C)

#Census Tracts
acsTractsCol.2019.sf <- get_acs(geography = "tract",
        year = 2019,
        variables = Variables$name, 
        state="Colorado",
        county= c("Boulder"),
        geometry=T,
        output = "wide") %>% 
  st_transform('ESRI:102653') %>%
  dplyr::select (GEOID, NAME, all_of(paste0(Variables$name,"E")))

#Unified School District
acsShoolDistrctssCol.2019.sf <- get_acs(geography = "school district (unified)",
        year = 2019,
        variables = Variables$name, 
        state="Colorado",
        geometry=T,
        output = "wide") %>% 
  st_transform('ESRI:102653') %>%
  dplyr::select (GEOID, NAME, all_of(paste0(Variables$name,"E")))

school_districts <- st_overlaps(st_union(acsTractsCol.2019.sf), acsShoolDistrctssCol.2019.sf )
acsShoolDistrctssCol.2019.sf <- acsShoolDistrctssCol.2019.sf %>%
  slice(school_districts[[1]])

district <- st_intersects(acsShoolDistrctssCol.2019.sf %>%
  slice(1),
  studentData.training)

studentData.training <- studentData.training %>%
                            mutate(Session = row_number(),
                            District1 = ifelse(Session %in% district[[1]], "District1", "NO"))

district <- st_intersects(acsShoolDistrctssCol.2019.sf %>%
  slice(2),
  studentData.training)

studentData.training <- studentData.training %>%
                            mutate(District2 = ifelse(Session %in% district[[1]], "District2", "NO"))

district <- st_intersects(acsShoolDistrctssCol.2019.sf %>%
  slice(3),
  studentData.training)

studentData.training <- studentData.training %>%
                           mutate(District3 = ifelse(Session %in% district[[1]], "District3", "NO"))

district <- st_intersects(acsShoolDistrctssCol.2019.sf %>%
  slice(4),
  studentData.training)

studentData.training <- studentData.training %>%
                           mutate(District4 = ifelse(Session %in% district[[1]], "District4", "NO"))

A <- studentData.training %>%
  select(50:54) %>%
  pivot_longer(cols = 2:5, names_to = "District") %>%
  filter(!value == "NO") %>%
  select(1:3)

studentData.training <- st_join(studentData.training, A, by = "Session") %>%
  select(-c("District1","District2","District3","District4","Session.x","Session.y"))

ggplot() +
  geom_sf(data = acsShoolDistrctssCol.2019.sf,
          fill = "red") +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent")

#Zip Code
acsZipsCol.2019.sf <- get_acs(geography = "zcta",
        year = 2019,
        variables = Variables$name, 
        geometry=T,
        output = "wide") %>% 
  st_transform('ESRI:102653') %>%
  dplyr::select (GEOID, NAME, all_of(paste0(Variables$name,"E")))

zipcodes <- st_overlaps(st_union(acsTractsCol.2019.sf), acsZipsCol.2019.sf)
acsZipsCol.2019.sf <- acsZipsCol.2019.sf %>%
  slice(zipcodes[[1]])

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(1),
  studentData.training)

studentData.training <- studentData.training %>%
                            mutate(Session = row_number(),
                                   Zip1 = ifelse(Session %in% district[[1]], "Zip1", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(2),
  studentData.training)

studentData.training <- studentData.training %>%
                            mutate(Zip2 = ifelse(Session %in% district[[1]], "Zip2", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(3),
  studentData.training)

studentData.training <- studentData.training %>%
                           mutate(Zip3 = ifelse(Session %in% district[[1]], "Zip3", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(4),
  studentData.training)

studentData.training <- studentData.training %>%
                           mutate(Zip4 = ifelse(Session %in% district[[1]], "Zip4", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(5),
  studentData.training)

studentData.training <- studentData.training %>%
                            mutate(Zip5 = ifelse(Session %in% district[[1]], "Zip5", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(6),
  studentData.training)

studentData.training <- studentData.training %>%
                            mutate(Zip6 = ifelse(Session %in% district[[1]], "Zip6", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(7),
  studentData.training)

studentData.training <- studentData.training %>%
                           mutate(Zip7 = ifelse(Session %in% district[[1]], "Zi73", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(8),
  studentData.training)

studentData.training <- studentData.training %>%
                           mutate(Zip8 = ifelse(Session %in% district[[1]], "Zip8", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(9),
  studentData.training)

studentData.training <- studentData.training %>%
                            mutate(Zip9 = ifelse(Session %in% district[[1]], "Zip9", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(10),
  studentData.training)

studentData.training <- studentData.training %>%
                            mutate(Zip10 = ifelse(Session %in% district[[1]], "Zip10", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(11),
  studentData.training)

studentData.training <- studentData.training %>%
                           mutate(Zip11 = ifelse(Session %in% district[[1]], "Zip11", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(12),
  studentData.training)

studentData.training <- studentData.training %>%
                           mutate(Zip12 = ifelse(Session %in% district[[1]], "Zip12", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(13),
  studentData.training)

studentData.training <- studentData.training %>%
                            mutate(Zip13 = ifelse(Session %in% district[[1]], "Zip13", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(14),
  studentData.training)

studentData.training <- studentData.training %>%
                            mutate(Zip14 = ifelse(Session %in% district[[1]], "Zip14", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(15),
  studentData.training)

studentData.training <- studentData.training %>%
                           mutate(Zip15 = ifelse(Session %in% district[[1]], "Zip15", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(16),
  studentData.training)

studentData.training <- studentData.training %>%
                           mutate(Zip16 = ifelse(Session %in% district[[1]], "Zip16", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(17),
  studentData.training)

studentData.training <- studentData.training %>%
                            mutate(Zip17 = ifelse(Session %in% district[[1]], "Zip17", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(18),
  studentData.training)

studentData.training <- studentData.training %>%
                            mutate(Zip18 = ifelse(Session %in% district[[1]], "Zip18", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(19),
  studentData.training)

studentData.training <- studentData.training %>%
                           mutate(Zip19 = ifelse(Session %in% district[[1]], "Zip19", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(20),
  studentData.training)

studentData.training <- studentData.training %>%
                           mutate(Zip20 = ifelse(Session %in% district[[1]], "Zip20", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(21),
  studentData.training)

studentData.training <- studentData.training %>%
                            mutate(Zip21 = ifelse(Session %in% district[[1]], "Zip21", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(22),
  studentData.training)

studentData.training <- studentData.training %>%
                            mutate(Zip22 = ifelse(Session %in% district[[1]], "Zip22", "NO"))

district <- st_intersects(acsZipsCol.2019.sf %>%
  slice(23),
  studentData.training)

studentData.training <- studentData.training %>%
                           mutate(Zip23 = ifelse(Session %in% district[[1]], "Zip23", "NO"))

A <- studentData.training %>%
  select(50:73) %>%
  pivot_longer(cols = 2:23, names_to = "Zip") %>%
  filter(!value == "NO") %>%
  select(1:3)

studentData.training <- st_join(studentData.training, A, by = "Session") %>%
  select(-c("Zip1","Zip2","Zip3","Zip4","Zip5","Zip6","Zip7","Zip8","Zip9","Zip10",
            "Zip11","Zip12","Zip13","Zip14","Zip15","Zip16","Zip17","Zip18","Zip19","Zip20",
            "Zip21","Zip22","Zip23","Session.x"))

ggplot() +
  geom_sf(data = acsZipsCol.2019.sf,
          fill = "red") +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "grey")
```

Census 2018

CURRENTLY NOT RUNNING
```{r tidycensus_2018, eval=FALSE, include=FALSE}

#variables on frequency of Race
Variables <- load_variables(2018,
                            "acs5",
                            cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("RACE", concept)) %>%
  filter(!grepl("AGE", concept)) %>%
  slice(1:10)

#variable median age, men and women not by race
A <- load_variables(2018,
                    "acs5",
                    cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("MEDIAN", concept)) %>%
  slice(1:3)

#Median Household Income
B <- load_variables(2018,
                    "acs5",
                    cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("MEDIAN INCOME", concept)) %>%
  slice(1)

# Cost of living
C <- load_variables(2018,
                    "acs5",
                    cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("COST", concept)) %>%
  slice(1:19)

Variables <- bind_rows(Variables, A, B, C)

acsTractsCol.2018.sf <- get_acs(geography = "tract",
        year = 2018,
        variables = Variables$name, 
        state="Colorado",
        county= c("Boulder"),
        geometry=T,
        output = "wide") %>% 
  st_transform('ESRI:102728') %>%
  dplyr::select (GEOID, NAME, all_of(paste0(Variables$name,"E"))) %>%
  mutate(Year = 2018)

ggplot() +
  geom_sf(data = acsTractsCol.2018.sf)
```

# Fixed Effect Census tracts 

```{r}
Census_tracts <- unique(acsTractsCol.2019.sf$GEOID)
z <- st_intersection(studentData, acsTractsCol.2019.sf %>%
                  filter(GEOID == Census_tracts[1]))

```

Website available for data https://open-data.bouldercolorado.gov/ 

```{r colorado_data}
# Use CRS ESRI:102653 - Colorado State Plane North: https://spatialreference.org/ref/esri/102653/

# Locations of Rental Properties (by license)
## https://open-data.bouldercolorado.gov/datasets/92f70ea894ef47a582bb0d656aa4aa7d_0/explore?location=40.013774%2C-105.256817%2C16.81
rentalHomes <- st_read("https://opendata.arcgis.com/datasets/92f70ea894ef47a582bb0d656aa4aa7d_0.geojson") %>%
  st_transform('ESRI:102653')

ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = st_centroid(rentalHomes)) +
  labs(title = "Rental Homes")


# Locations of Accessory Dwelling Units
## https://open-data.bouldercolorado.gov/datasets/669935e6d13c406497cd9cbbbd7951b2_0/explore?location=40.023716%2C-105.253583%2C11.91
## For explanation on what ADU's are: https://planning.org/knowledgebase/accessorydwellings/ 
adus <- st_read("https://opendata.arcgis.com/datasets/669935e6d13c406497cd9cbbbd7951b2_0.geojson") %>%
  st_transform('ESRI:102653')

ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = adus) +
  labs(title = "Accessory Dwelling Units")


# Locations of 100 Year floodplain
## https://open-data.bouldercolorado.gov/datasets/bfc343d63cf54831810b983b36ce6872_3/explore?location=40.007803%2C-105.223741%2C12.50
## About this dataset: https://open-data.bouldercolorado.gov/datasets/bfc343d63cf54831810b983b36ce6872_3/about
flood <- st_read("https://opendata.arcgis.com/datasets/bfc343d63cf54831810b983b36ce6872_3.geojson") %>%
  st_transform('ESRI:102653')

ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = flood) +
  labs(title = "100 Year Floodplain")


# Locations of Zoning districts
## https://open-data.bouldercolorado.gov/datasets/e88004e26b9e42cfba32129fb8731f41_0/explore?location=40.025701%2C-105.239775%2C11.45
## City of Boulder Colorado Zoning Districts. Including residential, business, industrial, public, agricultural, mix of residential and business, residential mobile homes, main street area and mixed density residential.
zoning <- st_read("https://opendata.arcgis.com/datasets/e88004e26b9e42cfba32129fb8731f41_0.geojson") %>%
  st_transform('ESRI:102653')

ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = zoning) +
  labs(title = "Zoning Districts")


# Locations of 19 libraries 
## https://opendata-bouldercounty.hub.arcgis.com/datasets/libraries-2/explore?location=40.001009%2C-105.302539%2C11.28

Col_Library <- st_read("https://opendata.arcgis.com/datasets/7f4ea25ba87345e380d2e896611d2588_0.geojson") %>%
  st_transform(st_crs(acsTractsCol.2019.sf)) %>%
  select(c(Name, geometry))

Buffer_Library <- st_buffer(Col_Library, 10560) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend)

UnionBuffer_Library <- st_union(Buffer_Library)

ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = Col_Library) +
  geom_sf(data = UnionBuffer_Library,
          fill = "transparent") +
  labs(title = "library")

allTracts.rings <-
  st_join(st_centroid(dplyr::select(acsTractsCol.2019.sf, GEOID)), 
          multipleRingBuffer(Buffer_Library, 5280, 2640)) %>%
  st_drop_geometry() %>%
  left_join(dplyr::select(acsTractsCol.2019.sf, GEOID), 
            by=c("GEOID"="GEOID")) %>%
  st_sf()


#addresses for buildings https://open-data.bouldercolorado.gov/datasets/d63e537da54640bd967c2fedc4c99a92_0/explore?location=40.026211%2C-105.232810%2C11.82 
Addresses <- st_read("https://opendata.arcgis.com/datasets/d63e537da54640bd967c2fedc4c99a92_0.geojson") %>%
  st_transform('ESRI:102653')

ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = Addresses) +
  labs(title = "Addresses")

# Properties managed by parks and recreation polygons ## https://open-data.bouldercolorado.gov/datasets/fdfc0410e75c48b6b9e53cf94bdbe224_1/explore?location=40.026750%2C-105.234200%2C12.05 
Parks <- st_read("https://opendata.arcgis.com/datasets/fdfc0410e75c48b6b9e53cf94bdbe224_1.geojson")


# Urban trees
## https://open-data.bouldercolorado.gov/datasets/dbbae8bdb0a44d17934243b88e85ef2b_0/explore?location=40.015538%2C-105.275671%2C16.12
trees <- st_read("https://opendata.arcgis.com/datasets/dbbae8bdb0a44d17934243b88e85ef2b_0.geojson") %>%
    st_transform('ESRI:102653')

ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = trees) +
  labs(title = "Street Trees")


```

#Buffers

```{r}
# Grocery Stores from Data Axle
Grocery_Store <- read.csv("DataAxle_GroceryStores.csv") %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326, agr = "constant") %>%
  st_transform('ESRI:102653') 

Buffer_Grocery <- st_buffer(Grocery_Store, 5280) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend)

Buffer_Grocery_Union <- st_union(st_buffer(Grocery_Store, 5280) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend))

ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = Grocery_Store) +
    geom_sf(data = Buffer_Grocery,
          fill = "transparent") +
  labs(title = "Grocery_Stores")

Grocery.rings <-
  st_join(st_centroid(dplyr::select(acsTractsCol.2019.sf, GEOID)), 
          multipleRingBuffer(Buffer_Grocery, 5280, 2640)) %>%
  st_drop_geometry() %>%
  left_join(dplyr::select(acsTractsCol.2019.sf, GEOID), 
            by=c("GEOID"="GEOID")) %>%
  st_sf()


#Restaurants from DataAxle
Restaurants <- bind_rows(read.csv("DataAxle_Restaurants_1.csv"), read.csv("DataAxle_Restaurants_2.csv")) %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326, agr = "constant") %>%
  st_transform('ESRI:102653')

Buffer_Restaurants <- st_union(st_buffer(Restaurants, 5280) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend))


ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = Restaurants) +
    geom_sf(data = Buffer_Restaurants,
          fill = "transparent") +
  labs(title = "Restaurants")

#Education from DataAxle
Education <- read.csv("DataAxle_Education.csv") %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326, agr = "constant") %>%
  st_transform('ESRI:102653')

Buffer_Education <- st_union(st_buffer(Education, 5280) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend))


#Museums from DataAxle
Museums <- read.csv("DataAxle_Musuems.csv") %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326, agr = "constant") %>%
  st_transform('ESRI:102653')

Buffer_Museums <- st_union(st_buffer(Museums, 5280) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend))


```


#Nearest Neighbors

```{r}
## grovery Nearest Neighbor
st_c <- st_coordinates

## restaurante NN
studentData.training <- studentData.training %>%
  mutate(grocery_nn1 = nn_function(st_c(studentData.training), st_c(Grocery_Store), 1),
         grocery_nn2 = nn_function(st_c(studentData.training), st_c(Grocery_Store), 2),
         grocery_nn3 = nn_function(st_c(studentData.training), st_c(Grocery_Store), 3),
         grocery_nn4 = nn_function(st_c(studentData.training), st_c(Grocery_Store), 4),
         grocery_nn5 = nn_function(st_c(studentData.training), st_c(Grocery_Store), 5))

studentData.training <- studentData.training %>%
  mutate(restaurant_nn1 = nn_function(st_c(studentData.training), st_c(Restaurants), 1),
         restaurant_nn2 = nn_function(st_c(studentData.training), st_c(Restaurants), 2),
         restaurant_nn3 = nn_function(st_c(studentData.training), st_c(Restaurants), 3),
         restaurant_nn4 = nn_function(st_c(studentData.training), st_c(Restaurants), 4),
         restaurant_nn5 = nn_function(st_c(studentData.training), st_c(Restaurants), 5))

studentData.training <- studentData.training %>%
  mutate(Education_nn1 = nn_function(st_c(studentData.training), st_c(Education), 1),
         Education_nn2 = nn_function(st_c(studentData.training), st_c(Education), 2),
         Education_nn3 = nn_function(st_c(studentData.training), st_c(Education), 3),
         Education_nn4 = nn_function(st_c(studentData.training), st_c(Education), 4),
         Education_nn5 = nn_function(st_c(studentData.training), st_c(Education), 5))

studentData.training <- studentData.training %>%
  mutate(Museums_nn1 = nn_function(st_c(studentData.training), st_c(Museums), 1),
         Museums_nn2 = nn_function(st_c(studentData.training), st_c(Museums), 2),
         Museums_nn3 = nn_function(st_c(studentData.training), st_c(Museums), 3),
         Museums_nn4 = nn_function(st_c(studentData.training), st_c(Museums), 4),
         Museums_nn5 = nn_function(st_c(studentData.training), st_c(Museums), 5))
```

```{r Centroid, message=FALSE, warning=FALSE}
# Creating centroids

#Rather than pick a half mile (2640 feet) I chose to use a 2 mile radius. Since I am working with suburbs, homes are further away from the regional lines. 

# Buffers for stations
Buffers <- 
  rbind(
    st_buffer(NJtransit, 10560) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend),
    st_union(st_buffer(NJtransit, 10560)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer"))




Linebuffer <- rbind(
    st_buffer(NjTransit_Lines, 10560) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend),
    st_union(st_buffer(NjTransit_Lines, 10560)) %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer"))


ggplot() +
  geom_sf(data=Buffers) +
  geom_sf(data = Linebuffer) +
  geom_sf(data=NJtransit, 
          aes(colour = STATION), 
          show.legend = "point", size= 2) +
  geom_sf(data = NjTransit_Lines) +
  facet_wrap(~Legend) + 
  mapTheme()


selectCentroids <-
  st_centroid(acsTractsNJ.2019.sf)[Buffers,] %>%
    st_drop_geometry() %>%
    left_join(dplyr::select(acsTractsNJ.2019.sf, GEOID)) %>%
    st_sf() %>%
  mutate(Select_type = "Select by Centroid")
```

# Appendix

Data I don't know what to do with. 

```{r}
#addresses for buildings https://open-data.bouldercolorado.gov/datasets/d63e537da54640bd967c2fedc4c99a92_0/explore?location=40.026211%2C-105.232810%2C11.82 
Addresses <- st_read("https://opendata.arcgis.com/datasets/d63e537da54640bd967c2fedc4c99a92_0.geojson") %>%
  st_transform('ESRI:102286')

ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = Addresses) +
  labs(title = "Addresses")
```





Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

