---
title: "Hedonic Home Price Prediction"
author: "Jonathon Sun, Johnathan Clementi a.k.a. John^2"
date: "9/29/2021"
output: html_document
---


```{r setup, include=FALSE, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(warning = FALSE)

pacman::p_load(tidyverse, tidycensus, sf, kableExtra, tmap, viridis, gridExtra, spdep, caret, ckanr, FNN, grid, gridExtra, ggcorplot, httr, sf, zipcodeR)
library(ggcorrplot)


options(scipen = 999)
options(scipen =  "sf")

source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

palette5 <- c("#25CB10", "#5AB60C", "#8FA108",   "#C48C04", "#FA7800")
```

# Introduction
  The intent of this report is to use local intelligence to improve zillow's predictive model utilizing only OLS regression. What we did to improve the model was include [INSERT VARAIBLES HERE].

# Data
  We were first given a dataset that included housing prices and the points where they were located. From here, we decided to organize our data between fixed-effect and nearest neighbors. Fixed-effects take into consideration points that lie within a designated boundary. For example, all houses in a particular zip code would undergo a similar fixed-effect because they all inhabit that zip code. In contrast, the nearest neighbor calculates the distance between two points and takes the average of those distances by nearest neighbor value [EXPAND ON THIS LATER]. 

#### Home prices dataset
```{r housedata, message=FALSE, warning=FALSE, include=FALSE}
# Set CRS for project
CO_statePlaneCentral = "ESRI:102254"

studentData <- st_read("studentData.geojson", crs = CO_statePlaneCentral) %>%
  mutate(pricePerSF = price/TotalFinishedSF,
         age = 2021 - builtYear,
         iprvmntAge = EffectiveYear - builtYear) %>%
  # Change NA address values to something R won't get rid of when we do na.omit()
  mutate(address=replace_na(address,"No address given")) %>%
  # Remove numeric categorical vars - there are already descriptions for these values in the df
  dplyr::select(-Stories, -UnitCount, -Ac, -Heating, -ExtWallPrim, -ExtWallSec, -IntWall, -Roof_Cover, -status_cd) %>%
  st_transform(CO_statePlaneCentral) 

studentData$pricePerSF <- as.integer(studentData$pricePerSF)

# Check to see we aren't loosing records
# testTrain <- studentData.training %>% na.omit()
# addition <- rbind(studentData.training,testTrain)
# difference <- addition[! duplicated(addition, fromLast = TRUE) & seq(nrow(addition)) <= nrow(studentData.training), ]
```


#### Census 2019
The first fixed effect variables that we looked at was census tract. Although, we are  
```{r tidycensus_2019, echo=FALSE, message=FALSE, warning=FALSE}

#variables on frequency of Race
Variables <- load_variables(2019,
                            "acs5",
                            cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("RACE", concept)) %>%
  filter(!grepl("AGE", concept)) %>%
  slice(1:10)

#variable median age, men and women not by race
A <- load_variables(2019,
                    "acs5",
                    cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("MEDIAN", concept)) %>%
  slice(1:3)

#Median Household Income
B <- load_variables(2019,
                    "acs5",
                    cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("MEDIAN INCOME", concept)) %>%
  slice(1)

# Cost of living
C <- load_variables(2019,
                    "acs5",
                    cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("COST", concept)) %>%
  slice(1:19)

Variables <- bind_rows(Variables, A, B, C)

# Pull census data using tidycensus
# Read in census tracts

acsTractsCol.2019.sf <- get_acs(geography = "tract",
        year = 2019,
        variables = Variables$name, 
        state="Colorado",
        county= c("Boulder"),
        geometry=T,
        output = "wide") %>% 
  st_transform(CO_statePlaneCentral)%>%
  dplyr::select (GEOID, NAME, all_of(paste0(Variables$name,"E"))) %>%
  rename(Total_pop = Variables$Merge_name[1],
         White_pop = Variables$Merge_name[2],
         Black_pop = Variables$Merge_name[3],
         American_Indian_pop = Variables$Merge_name[4],
         Asian_pop = Variables$Merge_name[5],
         Hawiian_PI_pop = Variables$Merge_name[6],
         OtherRace_pop = Variables$Merge_name[7],
         two_or_more_pop = Variables$Merge_name[8],
         two_other_pop = Variables$Merge_name[9],
         two_or_more_exclude_pop = Variables$Merge_name[10],
         Median_age = Variables$Merge_name[11],
         Median_Male_age = Variables$Merge_name[12],
         Median_Female_age = Variables$Merge_name[13],
         MortgagesTotal_mortgage = Variables$Merge_name[14],
         MortgagesHas_mortgage = Variables$Merge_name[15],
         Mortgage200Less_mortgage = Variables$Merge_name[16],
         Mortgage200_299_mortgage = Variables$Merge_name[17],
         Mortgage300_399_mortgage = Variables$Merge_name[18],
         Mortgage400_499_mortgage = Variables$Merge_name[19],
         Mortgage500_599_mortgage = Variables$Merge_name[20],
         Mortgage600_699_mortgage = Variables$Merge_name[21],
         Mortgage700_799_mortgage = Variables$Merge_name[22],
         Mortgage800_899_mortgage = Variables$Merge_name[23],
         Mortgage900_999_mortgage = Variables$Merge_name[24],
         Mortgage1000_1249_mortgage = Variables$Merge_name[25],
         Mortgage1250_1499_mortgage = Variables$Merge_name[26],
         Mortgage1500_1999_mortgage = Variables$Merge_name[27],
         Mortgage2000_2499_mortgage = Variables$Merge_name[28],
         Mortgage2500_2999_mortgage = Variables$Merge_name[29],
         Mortgage3000_3499_mortgage = Variables$Merge_name[30],
         Mortgage3500_3999_mortgage = Variables$Merge_name[31],
         Mortgage3750_3999_mortgage = Variables$Merge_name[32],
         Mortgage4000_mortgage = Variables$Merge_name[33]) 
         

  ggplot() +
  geom_sf(data = acsTractsCol.2019.sf)

# Read in census Block groups
 acsBGCol.2019.sf <- get_acs(geography = "block group",
         year = 2019,
         variables = Variables$name, 
         state="Colorado",
         county= c("Boulder"),
         geometry=T,
         output = "wide") %>% 
   st_transform(CO_statePlaneCentral) %>%
   dplyr::select (GEOID, NAME, all_of(paste0(Variables$name,"E")))
 
 ggplot() +
   geom_sf(data = acsBGCol.2019.sf)+
   labs(title = "Census Block Groups, Boulder County, Colorado")

 
 
studentData <- studentData %>%
  mutate(
    tracts = as.integer(st_intersects(geometry,acsTractsCol.2019.sf)))
# Assign a school district to each home
# Help document: https://gis.stackexchange.com/questions/133625/checking-if-points-fall-within-polygon-shapefile
studentData <- studentData %>%
  mutate(
    tracts = as.integer(st_intersects(geometry,acsTractsCol.2019.sf)))
    #,
    #schoolDist_name = if_else(is.na(District), "", acsSchoolDistrctssCol.2019.sf$NAME[District])

```


## Birds of a feather flock together

### Census Tracts by Race

q3 is the census tracts that have a median amount of white people. As a fixed effect, this would say for census tracts with the median amount of white people, what does the price look like?
q4_5 is census tracts that have above the median amount of white people. 
q1_3 is census tracts that have less then the median amount of white people

This disadvantage to using fixed effects is that they have to be binary, either they do or do not contain something, so in the case of race I used below the median, above the median and median as binaried functions. 

```{r eval=FALSE, include=FALSE}
# I did more work than I had to. I'm remaking this to just have factored quartiles. This block does not run so no worries. 

acsTractsCol.2019.sf <- acsTractsCol.2019.sf %>% 
  mutate(White_Quartile = q5(acsTractsCol.2019.sf$White_pop),
         Black_Quartile = q5(acsTractsCol.2019.sf$Black_pop),
         Asian_Quartile = q5(acsTractsCol.2019.sf$Asian_pop),
         American_Indian_Quartile = q5(acsTractsCol.2019.sf$American_Indian_pop),
         Hawiian_PI_Quartile = q5(acsTractsCol.2019.sf$Hawiian_PI_pop),
         OtherRace_Quartile = q5(acsTractsCol.2019.sf$OtherRace_pop),
         two_or_more_Quartile = q5(acsTractsCol.2019.sf$two_or_more_pop),
         two_other_Quartile = q5(acsTractsCol.2019.sf$two_other_pop),
         two_or_more_exclude_Quartile = q5(acsTractsCol.2019.sf$two_or_more_exclude_pop))

White <- acsTractsCol.2019.sf %>% 
  select(GEOID, White_pop) %>%
  mutate(White_Quartile = q5(acsTractsCol.2019.sf$White_pop))

Black <- acsTractsCol.2019.sf %>% 
  select(GEOID, Black_pop) %>%
  mutate(Black_Quartile = q5(acsTractsCol.2019.sf$Black_pop))

Asian <- acsTractsCol.2019.sf %>% 
  select(GEOID, Asian_pop) %>%
  mutate(Asian_Quartile = q5(acsTractsCol.2019.sf$Asian_pop))

American_Indian <- acsTractsCol.2019.sf %>% 
  select(GEOID, American_Indian_pop) %>%
  mutate(American_Indian_Quartile = q5(acsTractsCol.2019.sf$American_Indian_pop))

Hawiian_PI <- acsTractsCol.2019.sf %>% 
  select(GEOID, Hawiian_PI_pop) %>%
  mutate(Hawiian_PI_Quartile = q5(acsTractsCol.2019.sf$Hawiian_PI_pop))

OtherRace <- acsTractsCol.2019.sf %>% 
  select(GEOID, OtherRace_pop) %>%
  mutate(OtherRace_Quartile = q5(acsTractsCol.2019.sf$OtherRace_pop))

two_or_more <- acsTractsCol.2019.sf %>% 
  select(GEOID, two_or_more_pop) %>%
  mutate(two_or_more _Quartile = q5(acsTractsCol.2019.sf$two_or_more_pop))

two_other <- acsTractsCol.2019.sf %>% 
  select(GEOID, two_other_pop) %>%
  mutate(two_other_Quartile = q5(acsTractsCol.2019.sf$two_other_pop))

two_or_more_exclude <- acsTractsCol.2019.sf %>% 
  select(GEOID, two_or_more_exclude_pop) %>%
  mutate(two_or_more_exclude_Quartile = q5(acsTractsCol.2019.sf$two_or_more_exclude_pop))

```




```{r Race_don'trun, eval=FALSE, include=FALSE}
# I did more work than I had to. I'm remaking this to just have factored quartiles. This block does not run so no worries. 

White <- acsTractsCol.2019.sf %>% 
  select(GEOID, White_pop) %>%
  mutate(Quartile = as.numeric(q5(acsTractsCol.2019.sf$White_pop)),
         Race_Whiteq3 = ifelse(Quartile == 3, TRUE, FALSE),
         Race_Whiteq4_5 = ifelse(Quartile > 3, TRUE, FALSE),
         Race_Whiteq1_2 = ifelse(Quartile < 3, TRUE, FALSE))

Black <- acsTractsCol.2019.sf %>% 
  select(GEOID, Black_pop) %>%
  mutate(Quartile = as.numeric(q5(acsTractsCol.2019.sf$Black_pop)),
         Race_Blackq3 = ifelse(Quartile == 3, TRUE, FALSE),
         Race_Blackq4_5 = ifelse(Quartile > 3, TRUE, FALSE),
         Race_Blackq1_2 = ifelse(Quartile < 3, TRUE, FALSE))

Asian <- acsTractsCol.2019.sf %>% 
  select(GEOID, Asian_pop) %>%
  mutate(Quartile = as.numeric(q5(acsTractsCol.2019.sf$Asian_pop)),
         Race_Asianq3 = ifelse(Quartile == 3, TRUE, FALSE),
         Race_Asianq4_5 = ifelse(Quartile > 3, TRUE, FALSE),
         Race_Asianq1_2 = ifelse(Quartile < 3, TRUE, FALSE))

American_Indian <- acsTractsCol.2019.sf %>% 
  select(GEOID, American_Indian_pop) %>%
  mutate(Quartile = as.numeric(q5(acsTractsCol.2019.sf$American_Indian_pop)),
         Race_American_Indianq3 = ifelse(Quartile == 3, TRUE, FALSE),
         Race_American_Indianq4_5 = ifelse(Quartile > 3, TRUE, FALSE),
         Race_American_Indianq1_2 = ifelse(Quartile < 3, TRUE, FALSE))

Hawiian_PI <- acsTractsCol.2019.sf %>% 
  select(GEOID, Hawiian_PI_pop) %>%
  mutate(Quartile = as.numeric(q5(acsTractsCol.2019.sf$Hawiian_PI_pop)),
         Race_Hawiian_PIq3 = ifelse(Quartile == 3, TRUE, FALSE),
         Race_Hawiian_PIq4_5 = ifelse(Quartile > 3, TRUE, FALSE),
         Race_Hawiian_PIq1_2 = ifelse(Quartile < 3, TRUE, FALSE))

OtherRace <- acsTractsCol.2019.sf %>% 
  select(GEOID, OtherRace_pop) %>%
  mutate(Quartile = as.numeric(q5(acsTractsCol.2019.sf$OtherRace_pop)),
         RaceOther_Raceq3 = ifelse(Quartile == 3, TRUE, FALSE),
         RaceOther_Raceq4_5 = ifelse(Quartile > 3, TRUE, FALSE),
         RaceOther_Raceq1_2 = ifelse(Quartile < 3, TRUE, FALSE))

two_or_more <- acsTractsCol.2019.sf %>% 
  select(GEOID, two_or_more_pop) %>%
  mutate(Quartile = as.numeric(q5(acsTractsCol.2019.sf$two_or_more_pop)),
         Race_two_or_moreq3 = ifelse(Quartile == 3, TRUE, FALSE),
         Race_two_or_moreq4_5 = ifelse(Quartile > 3, TRUE, FALSE),
         Race_two_or_moreq1_2 = ifelse(Quartile < 3, TRUE, FALSE))

two_other <- acsTractsCol.2019.sf %>% 
  select(GEOID, two_other_pop) %>%
  mutate(Quartile = as.numeric(q5(acsTractsCol.2019.sf$two_other_pop)),
         Race_two_otherq3 = ifelse(Quartile == 3, TRUE, FALSE),
         Race_two_otherq4_5 = ifelse(Quartile > 3, TRUE, FALSE),
         Race_two_otherq1_2 = ifelse(Quartile < 3, TRUE, FALSE))

two_or_more_exclude <- acsTractsCol.2019.sf %>% 
  select(GEOID, two_or_more_exclude_pop) %>%
  mutate(Quartile = as.numeric(q5(acsTractsCol.2019.sf$two_or_more_exclude_pop)),
         Race_two_or_more_excludeq3 = ifelse(Quartile == 3, TRUE, FALSE),
         Race_two_or_more_excludeq4_5 = ifelse(Quartile > 3, TRUE, FALSE),
         Race_two_or_more_excludeq1_2 = ifelse(Quartile < 3, TRUE, FALSE))

```


Census 2018 - already have 2019 data, here because we don't want to get rid of the code
```{r tidycensus_2018, eval=FALSE, include=FALSE}

#variables on frequency of Race
Variables <- load_variables(2018,
                            "acs5",
                            cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("RACE", concept)) %>%
  filter(!grepl("AGE", concept)) %>%
  slice(1:10)

#variable median age, men and women not by race
A18 <- load_variables(2018,
                    "acs5",
                    cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("MEDIAN", concept)) %>%
  slice(1:3)

#Median Household Income
B18 <- load_variables(2018,
                    "acs5",
                    cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("MEDIAN INCOME", concept)) %>%
  slice(1)

# Cost of living
C18 <- load_variables(2018,
                    "acs5",
                    cache = TRUE) %>%
  mutate(Merge_name = paste(name,"E", sep ="")) %>%
  filter(grepl("COST", concept)) %>%
  slice(1:19)

Variables <- bind_rows(Variables, A18, B18, C18)

acsTractsCol.2018.sf <- get_acs(geography = "tract",
        year = 2018,
        variables = Variables$name, 
        state="Colorado",
        county= c("Boulder"),
        geometry=T,
        output = "wide") %>% 
  st_transform(CO_statePlaneCentral) %>%
  dplyr::select (GEOID, NAME, all_of(paste0(Variables$name,"E"))) %>%
  mutate(Year = 2018)

ggplot() +
  geom_sf(data = acsTractsCol.2018.sf)
```

#### Fixed Effect Census tracts 
```{r}
Census_tracts <- unique(acsTractsCol.2019.sf$GEOID)
z <- st_intersection(studentData, acsTractsCol.2019.sf %>%
                  filter(GEOID == Census_tracts[1]))
```


#### Boulder County School Districts
```{r school_districts, message=FALSE, warning=FALSE}
#Unified School District
acsSchoolDistrctssCol.2019.sf <- get_acs(geography = "school district (unified)",
        year = 2019,
        variables = Variables$name, 
        state="Colorado",
        geometry=T,
        output = "wide") %>% 
  st_transform(CO_statePlaneCentral) %>%
  dplyr::select (GEOID, NAME, all_of(paste0(Variables$name,"E")))

school_districts <- st_overlaps(st_union(acsTractsCol.2019.sf), acsSchoolDistrctssCol.2019.sf)
acsSchoolDistrctssCol.2019.sf <- acsSchoolDistrctssCol.2019.sf %>%
  slice(school_districts[[1]])


# Assign a school district to each home
# Help document: https://gis.stackexchange.com/questions/133625/checking-if-points-fall-within-polygon-shapefile
studentData <- studentData %>%
  mutate(
    District = paste0("District",as.integer(st_intersects(geometry,acsSchoolDistrctssCol.2019.sf)))
    #,
    #schoolDist_name = if_else(is.na(District), "", acsSchoolDistrctssCol.2019.sf$NAME[District])
  )


#ggplot() +
#  geom_sf(data = acsSchoolDistrctssCol.2019.sf,
#          fill = "red") +
#  geom_sf(data = st_union(acsTractsCol.2019.sf),
#         fill = "transparent")
```


#### Boulder City Fixed Effect
```{r city_Limits}
boulderCityLimits <- st_read("https://opendata.arcgis.com/datasets/955e7a0f52474b60a9866950daf10acb_0.geojson") %>%
  st_transform(st_crs(acsTractsCol.2019.sf)) %>%
  mutate(inCity = 1)

# Determine if a house is within the city or not - used for cases in which only city data is available
studentData <- studentData %>%
  mutate(withinCity = as.integer(st_intersects(geometry,boulderCityLimits)))

studentData <- studentData %>%
  mutate(withinCity = replace_na(withinCity,"0"))

# Change 
studentData <- studentData %>%
  mutate(withinCity = ifelse(withinCity > 0, 1, 0))

zips <- c(80301:80305)
zips <- as.character(zips)

ggplot() +
  geom_sf(data = acsZipsCol.2019.sf %>%
            filter(zipcode %in% zips)) +
  geom_sf(data = studentData) +
  geom_sf(data = boulderCityLimits,
          fill = "transparent",
          border = 2)
```


#### Boulder County Zip codes
```{r Zip_codes, eval=FALSE, warning=FALSE, include=FALSE}

#Zip Code
acsZipsCol.2019.sf <- get_acs(geography = "zcta",
        year = 2019,
        variables = Variables$name, 
        geometry=T,
        output = "wide") %>% 
  st_transform(CO_statePlaneCentral) %>%
  dplyr::select (GEOID, NAME, all_of(paste0(Variables$name,"E")))


acsZipsCol.2019.sf <- acsZipsCol.2019.sf %>%
  st_intersection(st_union(acsTractsCol.2019.sf)) %>%
  st_sf()

# # boulderCo_flood <- COState_flood %>%
# #   st_intersection(st_union(acsTractsCol.2019.sf)) %>%
# #   st_sf()


ggplot() +
  geom_sf(data = acsZipsCol.2019.sf) +
  geom_sf(data = studentData)

# zuocodeR package
acsZipsCol.2019 <- search_county('Boulder', 'CO') 

#ggplot() +
#  geom_sf(data = acsZipsCol.2019)

# Assign a zipcode to each home
# Help document: https://gis.stackexchange.com/questions/133625/checking-if-points-fall-within-polygon-shapefile
studentData <- studentData %>%
  mutate(
    Zip = paste0("Zip",as.integer(st_intersects(geometry,acsZipsCol.2019.sf)))
    #,
    #zipcode = if_else(is.na(Zip), "", acsSchoolDistrctssCol.2019.sf$NAME[Zip])
  )

ggplot() +
  geom_sf(data = acsZipsCol.2019.sf) +
  labs(title = "Zip Tracts, Boulder County, Colorado")

```


#### External factors

Website available for data https://open-data.bouldercolorado.gov/ 
```{r colorado_data, message=TRUE, warning=FALSE}

# # Locations of Rental Properties (by license)
# ## https://open-data.bouldercolorado.gov/datasets/92f70ea894ef47a582bb0d656aa4aa7d_0/explore?location=40.013774%2C-105.256817%2C16.81
# rentalHomes <- st_read("https://opendata.arcgis.com/datasets/92f70ea894ef47a582bb0d656aa4aa7d_0.geojson") %>%
#   st_transform(CO_statePlaneCentral)
# 
# ggplot() +
#   geom_sf(data = st_union(acsTractsCol.2019.sf),
#           fill = "transparent") +
#   geom_sf(data = st_centroid(rentalHomes)) +
#   labs(title = "Rental Homes")
# 
# 
# # Locations of Accessory Dwelling Units
# ## https://open-data.bouldercolorado.gov/datasets/669935e6d13c406497cd9cbbbd7951b2_0/explore?location=40.023716%2C-105.253583%2C11.91
# ## For explanation on what ADU's are: https://planning.org/knowledgebase/accessorydwellings/ 
# adus <- st_read("https://opendata.arcgis.com/datasets/669935e6d13c406497cd9cbbbd7951b2_0.geojson") %>%
#   st_transform(CO_statePlaneCentral)
# 
# ggplot() +
#   geom_sf(data = st_union(acsTractsCol.2019.sf),
#           fill = "transparent") +
#   geom_sf(data = adus) +
#   labs(title = "Accessory Dwelling Units")
# 
# 
```

```{r floodplains}
# Locations of 100 Year floodplain within Boulder County
# Data originally for the whole state, subsetted to Boulder County via st_intersect
## https://geo.colorado.edu/catalog/47540-5ca228ffd43267000b8c7448
## About this dataset: https://open-data.bouldercolorado.gov/datasets/bfc343d63cf54831810b983b36ce6872_3/about

# # Process for creating Boulder County Flood Plains shp
# COState_flood <- st_read("CO_state_100yrFloodplains.geojson") %>%
#   st_transform(CO_statePlaneCentral)
#
# boulderCo_flood <- COState_flood %>%
#   st_intersection(st_union(acsTractsCol.2019.sf)) %>%
#   st_sf()
#
# # Create Geopackage for ease of transport - only one file
# st_write(boulderCo_flood, "boulderCo_100yrFloodZones.gpkg")

boulderCo_flood_gpkg <- st_read("boulderCo_100yrFloodZones.gpkg")

# Convert floodplain polygons to polylines
flood_boundaries <- st_boundary(boulderCo_flood_gpkg)

# Sample flood boundaries to get point data (used to pass to the nearest neighbor function)
flood_pts <- st_sample(flood_boundaries, size = 500, type = 'regular')
flood_pts <- st_cast(flood_pts, 'POINT')

ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = flood_pts, aes(color = "Blue")) +
  geom_sf(data = studentData)

```

```{r} 
# # Locations of Zoning districts
# ## https://open-data.bouldercolorado.gov/datasets/e88004e26b9e42cfba32129fb8731f41_0/explore?location=40.025701%2C-105.239775%2C11.45
# ## City of Boulder Colorado Zoning Districts. Including residential, business, industrial, public, agricultural, mix of residential and business, residential mobile homes, main street area and mixed density residential.
# zoning <- st_read("https://opendata.arcgis.com/datasets/e88004e26b9e42cfba32129fb8731f41_0.geojson") %>%
#   st_transform(CO_statePlaneCentral)
# 
# ggplot() +
#   geom_sf(data = st_union(acsTractsCol.2019.sf),
#           fill = "transparent") +
#   geom_sf(data = zoning) +
#   labs(title = "Zoning Districts")


# Locations of 19 libraries 
## https://opendata-bouldercounty.hub.arcgis.com/datasets/libraries-2/explore?location=40.001009%2C-105.302539%2C11.28
Col_Library <- st_read("https://opendata.arcgis.com/datasets/7f4ea25ba87345e380d2e896611d2588_0.geojson") %>%
  st_transform(st_crs(acsTractsCol.2019.sf)) %>%
  select(c(Name, geometry))

Buffer_Library <- st_buffer(Col_Library, 10560) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend)

UnionBuffer_Library <- st_union(Buffer_Library)


ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = Col_Library) +
  geom_sf(data = UnionBuffer_Library,
          fill = "transparent") +
  labs(title = "library")


#addresses for buildings https://open-data.bouldercolorado.gov/datasets/d63e537da54640bd967c2fedc4c99a92_0/explore?location=40.026211%2C-105.232810%2C11.82 
# Addresses <- st_read("https://opendata.arcgis.com/datasets/d63e537da54640bd967c2fedc4c99a92_0.geojson") %>%
#   st_transform(CO_statePlaneCentral)
# 
# ggplot() +
#   geom_sf(data = st_union(acsTractsCol.2019.sf),
#           fill = "transparent") +
#   geom_sf(data = Addresses) +
#   labs(title = "Addresses")

# Properties managed by parks and recreation polygons ## https://open-data.bouldercolorado.gov/datasets/fdfc0410e75c48b6b9e53cf94bdbe224_1/explore?location=40.026750%2C-105.234200%2C12.05 
Parks <- st_read("https://opendata.arcgis.com/datasets/fdfc0410e75c48b6b9e53cf94bdbe224_1.geojson")
ggplot() +
  geom_sf(data = acsTractsCol.2019.sf) +
  geom_sf(data = Parks,
          fill = "pink")

# Urban trees
## https://open-data.bouldercolorado.gov/datasets/dbbae8bdb0a44d17934243b88e85ef2b_0/explore?location=40.015538%2C-105.275671%2C16.12
trees <- st_read("https://opendata.arcgis.com/datasets/dbbae8bdb0a44d17934243b88e85ef2b_0.geojson") %>%
    st_transform(CO_statePlaneCentral)

ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = trees) +
  labs(title = "Street Trees")


```

## Feature Engineering


#### Buffers

```{r}
# Grocery Stores from Data Axle
Grocery_Store <- read.csv("DataAxle_GroceryStores.csv") %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326, agr = "constant") %>%
  st_transform(CO_statePlaneCentral) 

Buffer_Grocery <- st_buffer(Grocery_Store, 5280) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend)

Buffer_Grocery_Union <- st_union(st_buffer(Grocery_Store, 5280) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend))

ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = Grocery_Store) +
    geom_sf(data = Buffer_Grocery,
          fill = "transparent") +
  labs(title = "Grocery_Stores")

#Grocery.rings <-
#  st_join(st_centroid(dplyr::select(studentData, address)), 
#          multipleRingBuffer(Buffer_Grocery, 5280, 2640)) %>%
#  st_drop_geometry() %>%
#  left_join(dplyr::select(studentData, address), 
#            by=c("address"="address")) %>%
#  st_sf()

#Restaurants from DataAxle
Restaurants <- bind_rows(read.csv("DataAxle_Restaurants_1.csv"), read.csv("DataAxle_Restaurants_2.csv")) %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326, agr = "constant") %>%
  st_transform(CO_statePlaneCentral)

Buffer_Restaurants <- st_union(st_buffer(Restaurants, 5280) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend))


ggplot() +
  geom_sf(data = st_union(acsTractsCol.2019.sf),
          fill = "transparent") +
  geom_sf(data = Restaurants) +
    geom_sf(data = Buffer_Restaurants,
          fill = "transparent") +
  labs(title = "Restaurants")

#Education from DataAxle
Education <- read.csv("DataAxle_Education.csv") %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326, agr = "constant") %>%
  st_transform(CO_statePlaneCentral)

Buffer_Education <- st_union(st_buffer(Education, 5280) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend))


#Museums from DataAxle
Museums <- read.csv("DataAxle_Musuems.csv") %>%
  st_as_sf(coords = c("Longitude", "Latitude"), crs = 4326, agr = "constant") %>%
  st_transform(CO_statePlaneCentral)

Buffer_Museums <- st_union(st_buffer(Museums, 5280) %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend))


```


#### Nearest Neighbors

```{r message=FALSE, warning=FALSE, include=FALSE}
## grovery Nearest Neighbor
st_c <- st_coordinates

## restaurante NN
studentData <- studentData %>%
  mutate(grocery_nn1 = nn_function(st_c(studentData), st_c(Grocery_Store), 1),
         grocery_nn2 = nn_function(st_c(studentData), st_c(Grocery_Store), 2),
         grocery_nn3 = nn_function(st_c(studentData), st_c(Grocery_Store), 3),
         grocery_nn4 = nn_function(st_c(studentData), st_c(Grocery_Store), 4),
         grocery_nn5 = nn_function(st_c(studentData), st_c(Grocery_Store), 5))

studentData <- studentData %>%
  mutate(restaurant_nn1 = nn_function(st_c(studentData), st_c(Restaurants), 1),
         restaurant_nn2 = nn_function(st_c(studentData), st_c(Restaurants), 2),
         restaurant_nn3 = nn_function(st_c(studentData), st_c(Restaurants), 3),
         restaurant_nn4 = nn_function(st_c(studentData), st_c(Restaurants), 4),
         restaurant_nn5 = nn_function(st_c(studentData), st_c(Restaurants), 5))

studentData <- studentData %>%
  mutate(Education_nn1 = nn_function(st_c(studentData), st_c(Education), 1),
         Education_nn2 = nn_function(st_c(studentData), st_c(Education), 2),
         Education_nn3 = nn_function(st_c(studentData), st_c(Education), 3),
         Education_nn4 = nn_function(st_c(studentData), st_c(Education), 4),
         Education_nn5 = nn_function(st_c(studentData), st_c(Education), 5))

studentData <- studentData %>%
  mutate(Museums_nn1 = nn_function(st_c(studentData), st_c(Museums), 1),
         Museums_nn2 = nn_function(st_c(studentData), st_c(Museums), 2),
         Museums_nn3 = nn_function(st_c(studentData), st_c(Museums), 3),
         Museums_nn4 = nn_function(st_c(studentData), st_c(Museums), 4),
         Museums_nn5 = nn_function(st_c(studentData), st_c(Museums), 5))

studentData <- studentData %>%
  mutate(floodpts_nn1 = nn_function(st_c(studentData), st_c(flood_pts), 1),
         floodpts_nn2 = nn_function(st_c(studentData), st_c(flood_pts), 2),
         floodpts_nn3 = nn_function(st_c(studentData), st_c(flood_pts), 3),
         floodpts_nn4 = nn_function(st_c(studentData), st_c(flood_pts), 4),
         floodpts_nn5 = nn_function(st_c(studentData), st_c(flood_pts), 5))

studentData <- studentData %>%
  mutate(Library_nn1 = nn_function(st_c(studentData), st_c(Col_Library), 1),
         Library_nn2 = nn_function(st_c(studentData), st_c(Col_Library), 2),
         Library_nn3 = nn_function(st_c(studentData), st_c(Col_Library), 3),
         Library_nn4 = nn_function(st_c(studentData), st_c(Col_Library), 4),
         Library_nn5 = nn_function(st_c(studentData), st_c(Col_Library), 5))
```

# Methods

#### Exploratory analysis

Visualize price per sq foot
```{r}
# THIS IS WHERE WE CAN DIVERGE FROM TRAINING AND CHALLENGE DATASETS #

ggplot() +
  geom_sf(data = acsTractsCol.2019.sf, fill = "grey40") +
  geom_sf(data = studentData, aes(colour = q5(pricePerSF)), 
          show.legend = "point", size = .75) +
  scale_colour_manual(values = palette5,
                   labels=qBr(studentData,"pricePerSF"),
                   name="Quintile\nBreaks") +
  labs(title="Price Per Square Foot, Boulder Ccounty Colorado") +
  mapTheme()
```

Visualize price as a function of various continuous variables
```{r}
st_drop_geometry(studentData) %>% 
  dplyr::select(price, TotalFinishedSF, age, iprvmntAge) %>%
  filter(price <= 5000000, age < 500) %>%
  gather(Variable, Value, -price) %>% 
   ggplot(aes(Value, price)) +
     geom_point(size = .5) + geom_smooth(method = "lm", se=F, colour = "#FA7800") +
     facet_wrap(~Variable, ncol = 3, scales = "free") +
     labs(title = "Price as a function of continuous variables") +
     plotTheme()
```


# Present 4 home price correlation scatterplots that you think are of interest. I’m going to look for interesting open data that you’ve integrated with the home sale observations

```{r NN_Grocery_plots, echo=FALSE, message=FALSE, warning=FALSE}
max <- max(
  studentData %>%
  filter(toPredict == 0) %>%
  select(price) %>%
  st_drop_geometry())


st_drop_geometry(studentData) %>%
  filter(toPredict == 0) %>%
  filter(price < max) %>%
  select(1,MUSA_ID,starts_with("grocery")) %>%
  pivot_longer(cols = starts_with("grocery"), 
               names_to = "Nearest_Neighbor",
               values_to = "Distance") %>%
  group_by(Nearest_Neighbor, price) %>%
  summarize(mean_distance = mean(Distance)) %>%
  ggplot(aes(mean_distance,price)) +
    geom_point(size = .5) +
    geom_smooth(method = "lm", se = F, colour = "#FA7800") +
    facet_wrap(~Nearest_Neighbor) +
    labs(title = "Nearest Neighbor Grocery Store and Price") +
    plotTheme()
```


```{r NN_Restaurant_plots, echo=FALSE, message=FALSE, warning=FALSE}
st_drop_geometry(studentData) %>%
  filter(price < max) %>%
  select(1,MUSA_ID,starts_with("restaurant")) %>%
  pivot_longer(cols = starts_with("restaurant"), 
               names_to = "Nearest_Neighbor",
               values_to = "Distance") %>%
  group_by(Nearest_Neighbor, price) %>%
  summarize(mean_distance = mean(Distance)) %>%
  ggplot(aes(mean_distance,price)) +
    geom_point(size = .5) +
    geom_smooth(method = "lm", se = F, colour = "#FA7800") +
    facet_wrap(~Nearest_Neighbor) +
    labs(title = "Nearest Neighbor Restaurant and Price") +
    plotTheme()
```

```{r NN_Education_plots, echo=FALSE, message=FALSE, warning=FALSE}

st_drop_geometry(studentData) %>%
  filter(price < max) %>%
  select(1,MUSA_ID,starts_with("Education")) %>%
  pivot_longer(cols = starts_with("Education"), 
               names_to = "Nearest_Neighbor",
               values_to = "Distance") %>%
  group_by(Nearest_Neighbor, price) %>%
  summarize(mean_distance = mean(Distance)) %>%
  ggplot(aes(mean_distance,price)) +
    geom_point(size = .5) +
    geom_smooth(method = "lm", se = F, colour = "#FA7800") +
    facet_wrap(~Nearest_Neighbor) +
    labs(title = "Nearest Neighbor Grocery Store and Price") +
    plotTheme()
```

```{r NN_Museums_plots, echo=FALSE, message=FALSE, warning=FALSE}

st_drop_geometry(studentData) %>%
  filter(price < max) %>%
  select(1,MUSA_ID,starts_with("Museums")) %>%
  pivot_longer(cols = starts_with("Museums"), 
               names_to = "Nearest_Neighbor",
               values_to = "Distance") %>%
  group_by(Nearest_Neighbor, price) %>%
  summarize(mean_distance = mean(Distance)) %>%
  ggplot(aes(mean_distance,price)) +
    geom_point(size = .5) +
    geom_smooth(method = "lm", se = F, colour = "#FA7800") +
    facet_wrap(~Nearest_Neighbor) +
    labs(title = "Nearest Neighbor Grocery Store and Price") +
    plotTheme()
```


```{r ComparingNN1_plots, echo=FALSE, message=FALSE, warning=FALSE}

st_drop_geometry(studentData) %>%
  filter(price < max) %>%
  select(1,MUSA_ID, ends_with("nn1")) %>%
  pivot_longer(cols = ends_with("nn1"), 
               names_to = "Amenities",
               values_to = "Distance") %>%
  group_by(Amenities, price) %>%
  summarize(mean_distance = mean(Distance)) %>%
  ggplot(aes(mean_distance,price)) +
    geom_point(size = .5) +
    geom_smooth(method = "lm", se = F, colour = "#FA7800") +
    facet_wrap(~Amenities) +
    labs(title = "Nearest Neighbor Grocery Store and Price") +
    plotTheme()
```


```{r ComparingNN2_plots, echo=FALSE, message=FALSE, warning=FALSE}

st_drop_geometry(studentData) %>%
  filter(price < max) %>%
  select(1,MUSA_ID, ends_with("nn2")) %>%
  pivot_longer(cols = ends_with("nn2"), 
               names_to = "Amenities",
               values_to = "Distance") %>%
  group_by(Amenities, price) %>%
  summarize(mean_distance = mean(Distance)) %>%
  ggplot(aes(mean_distance,price)) +
    geom_point(size = .5) +
    geom_smooth(method = "lm", se = F, colour = "#FA7800") +
    facet_wrap(~Amenities) +
    labs(title = "Nearest Neighbor Grocery Store and Price") +
    plotTheme()
```

```{r ComparingNN3_plots, echo=FALSE, message=FALSE, warning=FALSE}

st_drop_geometry(studentData) %>%
  filter(price < max) %>%
  select(1,MUSA_ID, ends_with("nn3")) %>%
  pivot_longer(cols = ends_with("nn3"), 
               names_to = "Amenities",
               values_to = "Distance") %>%
  group_by(Amenities, price) %>%
  summarize(mean_distance = mean(Distance)) %>%
  ggplot(aes(mean_distance,price)) +
    geom_point(size = .5) +
    geom_smooth(method = "lm", se = F, colour = "#FA7800") +
    facet_wrap(~Amenities) +
    labs(title = "Nearest Neighbor Grocery Store and Price") +
    plotTheme()
```

```{r ComparingNN4_plots, echo=FALSE, message=FALSE, warning=FALSE}

st_drop_geometry(studentData) %>%
  filter(price < max) %>%
  select(1,MUSA_ID, ends_with("nn4")) %>%
  pivot_longer(cols = ends_with("nn4"), 
               names_to = "Amenities",
               values_to = "Distance") %>%
  group_by(Amenities, price) %>%
  summarize(mean_distance = mean(Distance)) %>%
  ggplot(aes(mean_distance,price)) +
    geom_point(size = .5) +
    geom_smooth(method = "lm", se = F, colour = "#FA7800") +
    facet_wrap(~Amenities) +
    labs(title = "Nearest Neighbor Grocery Store and Price") +
    plotTheme()
```

```{r ComparingNN5_plots, echo=FALSE, message=FALSE, warning=FALSE}

st_drop_geometry(studentData) %>%
  filter(price < max) %>%
  select(1,MUSA_ID, ends_with("nn5")) %>%
  pivot_longer(cols = ends_with("nn5"), 
               names_to = "Amenities",
               values_to = "Distance") %>%
  group_by(Amenities, price) %>%
  summarize(mean_distance = mean(Distance)) %>%
  ggplot(aes(mean_distance,price)) +
    geom_point(size = .5) +
    geom_smooth(method = "lm", se = F, colour = "#FA7800") +
    facet_wrap(~Amenities) +
    labs(title = "Nearest Neighbor Grocery Store and Price") +
    plotTheme()
```

```{r NN_Indicator, echo=FALSE, message=FALSE, warning=FALSE}
bind_rows(
  st_drop_geometry(studentData) %>%
  filter(price < max) %>%
  select(1,MUSA_ID, ends_with("nn1")) %>%
  select(!starts_with("flood_pts")) %>%
  mutate(nn = "nn1") %>%
  pivot_longer(cols = ends_with("nn1"), 
               names_to = "Amenities",
               values_to = "Distance"),
  st_drop_geometry(studentData) %>%
  filter(price < max) %>%
  select(1,MUSA_ID, ends_with("nn2")) %>%
  select(!starts_with("flood_pts")) %>%
      mutate(nn = "nn2") %>%
  pivot_longer(cols = ends_with("nn2"), 
               names_to = "Amenities",
               values_to = "Distance"),
  st_drop_geometry(studentData) %>%
  filter(price < max) %>%
  select(1,MUSA_ID, ends_with("nn3")) %>%
  select(!starts_with("flood_pts")) %>%
      mutate(nn = "nn3") %>%
  pivot_longer(cols = ends_with("nn3"), 
               names_to = "Amenities",
               values_to = "Distance"),
  st_drop_geometry(studentData) %>%
  filter(price < max) %>%
  select(1,MUSA_ID, ends_with("nn4")) %>%
  select(!starts_with("flood_pts")) %>%
      mutate(nn = "nn4") %>%
  pivot_longer(cols = ends_with("nn4"), 
               names_to = "Amenities",
               values_to = "Distance"),
  st_drop_geometry(studentData) %>%
  filter(price < max) %>%
  select(1,MUSA_ID, ends_with("nn5")) %>%
  select(!starts_with("flood_pts")) %>%
      mutate(nn = "nn5") %>%
  pivot_longer(cols = ends_with("nn5"), 
               names_to = "Amenities",
               values_to = "Distance")) %>%
  group_by(price, nn) %>%
  summarize(mean_distance = mean(Distance)) %>%
  ggplot(aes(mean_distance,price)) +
    geom_point(size = .5) +
    geom_smooth(method = "lm", se = F, colour = "#FA7800") +
    labs(title = "Amenities Nearest Neighbor Average and Price") +
  facet_wrap(~nn) +
    plotTheme()
```

Price as a function of categorical variables
```{r fig.height=15, fig.width=10, message=FALSE, warning=FALSE}
st_drop_geometry(studentData) %>% 
  dplyr::select(price, designCodeDscr, ConstCodeDscr, carStorageTypeDscr) %>%
  # mutate(NUM_FLOORS = as.factor(NUM_FLOORS)) %>%
  filter(price <= 5000000) %>%
  gather(Variable, Value, -price) %>% 
   ggplot(aes(Value, price)) +
     geom_bar(position = "dodge", stat = "summary", fun.y = "mean") +
     facet_wrap(~Variable, ncol = 1, scales = "free") +
     labs(title = "Price as a function of\ncategorical variables", y = "Mean_Price") +
     plotTheme() + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
st_drop_geometry(studentData) %>%
  select(price, District) %>%
  filter(price <= 5000000) %>%
  ggplot(aes(price, District)) +
  geom_bar(position = "dodge", stat = "summary", fun.y = "mean")
```

```{r}
st_drop_geometry(studentData) %>%
  filter(price <= 5000000) %>%
  group_by(Zip) %>%
  summarize(Frequency = n()) %>%
  arrange(desc(Zip))

```


```{r}
st_drop_geometry(studentData) %>%
  select(price, Zip) %>%
  filter(price <= 5000000) %>%
  ggplot(aes(price, Zip)) +
  geom_bar(position = "dodge", stat = "summary", fun.y = "mean")
```

```{r message=FALSE, warning=FALSE}
studentData.training <- studentData %>%
    filter(toPredict == 0)

studentData.challenge <- studentData %>%
    filter(toPredict == 1)

A <- bind_rows(
  st_drop_geometry(studentData.training) %>%
  filter(price < max(studentData.training$price)) %>%
  select(1,MUSA_ID, ends_with("nn1")) %>%
  select(!starts_with("flood_pts")) %>%
  mutate(nn = "nn1") %>%
  pivot_longer(cols = ends_with("nn1"), 
               names_to = "Amenities",
               values_to = "Distance"),
  st_drop_geometry(studentData.training) %>%
  filter(price < max(studentData.training$price)) %>%
  select(1,MUSA_ID, ends_with("nn2")) %>%
  select(!starts_with("flood_pts")) %>%
      mutate(nn = "nn2") %>%
  pivot_longer(cols = ends_with("nn2"), 
               names_to = "Amenities",
               values_to = "Distance"),
  st_drop_geometry(studentData.training) %>%
  filter(price < max(studentData.training$price)) %>%
  select(1,MUSA_ID, ends_with("nn3")) %>%
  select(!starts_with("flood_pts")) %>%
      mutate(nn = "nn3") %>%
  pivot_longer(cols = ends_with("nn3"), 
               names_to = "Amenities",
               values_to = "Distance"),
  st_drop_geometry(studentData.training) %>%
  filter(price < max(studentData.training$price)) %>%
  select(1,MUSA_ID, ends_with("nn4")) %>%
  select(!starts_with("flood_pts")) %>%
      mutate(nn = "nn4") %>%
  pivot_longer(cols = ends_with("nn4"), 
               names_to = "Amenities",
               values_to = "Distance"),
  st_drop_geometry(studentData.training) %>%
  filter(price < max(studentData.training$price)) %>%
  select(1,MUSA_ID, ends_with("nn5")) %>%
  select(!starts_with("flood_pts")) %>%
      mutate(nn = "nn5") %>%
  pivot_longer(cols = ends_with("nn5"), 
               names_to = "Amenities",
               values_to = "Distance")) %>%
  group_by(MUSA_ID) %>%
  summarize(mean_distance = mean(Distance))

studentData.training <- left_join(studentData.training, A, by = "MUSA_ID")

```


Correlation matrix
```{r message=FALSE, warning=FALSE}
numericVars <- studentData.training %>%
                  select(!starts_with("grocery")) %>%
                  select(!starts_with("restaurant")) %>%
                  select(!starts_with("Education")) %>%
                  select(!starts_with("Museums")) %>%
                  select(!starts_with("Library"))

numericVars <- 
  st_drop_geometry(numericVars) %>% 
  select(where(is.numeric)) %>%
  na.omit()

numericVars$mean_distance <- as.integer(numericVars$mean_distance)

numericVars <- numericVars %>%
  na.omit()

ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  colors = c("#25CB10", "white", "#FA7800"),
  type="lower",
  insig = "blank") +  
    labs(title = "Correlation across numeric variables")

#trying to find variables that have a correlation value between 0.5 and -0.5
res <- as.data.frame(cor(numericVars)) %>%
rownames_to_column()

#pivot longer and sort through list 

A <- res %>%
  select(!c("bldgClass","toPredict")) %>%
  slice(-c(6,21)) %>%
  pivot_longer(2:30) %>%
  filter(value >= 0.3 & value <0.5)

B <- res %>%
  select(!c("bldgClass","toPredict")) %>%
  slice(-c(6,21)) %>%
  pivot_longer(2:30) %>%
  filter(value >= -0.5 & value < -0.3)

corlist <- bind_rows(A,B)

corlist <- corlist %>%
  group_by(value) %>%
  arrange(desc(value))

#all odd numbers between 1 and 80
keep <- c(1:nrow(corlist))
keep <- which(keep %% 2 == 1)

corlist <- corlist %>%
             slice(keep) 

# includes all correlated with price
priceCor <- corlist %>%
  filter(rowname == "price")

keep <- priceCor$name

categorical <- c("Zip","District","price")
keep <- append(keep, categorical)


```

#### OLS
```{r warning=FALSE}
cor.test(studentData.training$mean_distance, studentData.training$price, method = "pearson")

cor.test(studentData.training$TotalFinishedSF, studentData.training$price, method = "pearson")

livingReg <- lm(price ~ TotalFinishedSF, data = studentData.training)

summary(livingReg)
```

### Multiple regression

```{r message=FALSE, warning=FALSE}
studentData.training %>%
  select(keep)

reg1 <- lm(price ~ ., data = st_drop_geometry(studentData.training) %>% 
       dplyr::select(keep))

summary(reg1)
```

### Testing accuracy using MAE & MAPE
```{r message=FALSE, warning=FALSE}
set.seed(5)

inTrain <- createDataPartition(
              y = paste(studentData.training$district,
                        studentData.training$designCode,
                        studentData.training$Zip),
              times = 1,
              p = .70, 
              list = FALSE)

training <- studentData.training[inTrain,] 
test <- studentData.training[-inTrain,]  

keep <- append(keep, "District")
reg.training <- lm(price ~ ., data = st_drop_geometry(training) %>% 
                                    dplyr::select(keep))

summary(reg.training)

test <- test %>%
  mutate(SalePrice.Predict = predict(reg.training, test),
         SalePrice.Error = SalePrice.Predict - price,
         SalePrice.AbsError = abs(SalePrice.Predict - price),
         SalePrice.APE = (abs(SalePrice.Predict - price)) / SalePrice.Predict)

mae <- mean(test$SalePrice.AbsError, na.rm=TRUE)
print(mae)
mape <- mean(test$SalePrice.APE, na.rm=TRUE)
print(mape)

```

### Do prices and errors cluster - spatial lag & testing for SA in our current model
```{r}
coords.test <-  st_coordinates(test) 

neighborList.test <- knn2nb(knearneigh(coords.test, 5))


spatialWeights.test <- nb2listw(neighborList.test, style="W")
 
test %>% 
  mutate(lagPriceError = lag.listw(spatialWeights.test, SalePrice.Error)) %>%
  ggplot(aes(lagPriceError, SalePrice.Error))
```


### Moran's I
```{r}
moranTest <- moran.mc(test$SalePrice.Error, 
                      spatialWeights.test, nsim = 999)

ggplot(as.data.frame(moranTest$res[c(1:999)]), aes(moranTest$res[c(1:999)])) +
  geom_histogram(binwidth = 0.01) +
  geom_vline(aes(xintercept = moranTest$statistic), colour = "#FA7800",size=1) +
  scale_x_continuous(limits = c(-1, 1)) +
  labs(title="Observed and permuted Moran's I",
       subtitle= "Observed Moran's I in orange",
       x="Moran's I",
       y="Count") +
  plotTheme()
```


# Results

# Discussion

# Conclusion

# Appendix


